From Stone to Tool: How Raw Materials Influenced Upper Paleolithic Technology in Southwestern Iberia (Vale Boi)

### 2025-06-19 analysis/paper/paper.qmd
Review corrections. Tweeks to the ggsave code.

#ggsave("gravettian_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")

@@

#ggsave("proto_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")

@@

#ggsave("solutrean_plots.png", width = 6, height = 6, units = "in", dpi = 300, bg = "white")

>>>>

#ggsave("gravettian_plots.png", width = 6, height = 7, units = "in", dpi = 300, bg = "white")

@@

#ggsave("proto_plots.png", width = 6, height = 7, units = "in", dpi = 300, bg = "white")

@@

#ggsave("solutrean_plots.png", width = 6, height = 7, units = "in", dpi = 300, bg = "white")
